An Efficient Calculus for Generalised Parikh Images of Regular Languages

### 2022-07-05 main.tex
conclusion

\contents{
  \item Future extensions: more logics
  \item Loop invariants?
  \item Integration into string solvers?
  \item We have shown fastest
  \item We have shown versatile
  \item We have shown concretely useful
}

>>>>

In this paper we have introduced an automated theorem prover-friendly calculus
to compute commutating operations on intersections of regular languages that we
call \Calculus{}. We have evaluated it on \NrBenchmarks{} Parikh automata
intersection problems generated \Fudge{by the Ostrich+} string solver
\cite{ostrich} solving \Fudge{standard string constraint benchmarks} using our
Parikh automata solver \Catra{}.

Within \Catra{}, \Calculus{} shows astonishing performance in terms of memory
usage and solve-time compared to the baseline approach laid out in
\cite{generate-parikh-image} when implemented on the same underlying automated
theorem prover (\Princess{}, \cite{princess}). It is also competitive with the
\Nuxmv{} model checker \cite{nuxmv}, outperforming it on unsatisfiable instances
and generally outperforming it for timeouts under 30 seconds with its advantage
increasing drastically for even shorter timeouts. 30 seconds would generally be
considered a long timeout for our intended use as supporting infrastructure to a
string constraint solver.

Future investigations involve two tracks. The first one is integration into
existing string solvers (wich \Ostrich{} being a particularly promising
candidate due to its shared use of \Princess{}), and further adaptation to that
use case. Closer inspection of the instances where we currently time out should
be useful to further improve our heuristics.

The second track for future improvements is the extension into other problem
domains, including other logics, model checking problems, as well as to more
powerful automata such as transducers. In principle, we are also already able to
express stronger constraints than Parikh automata, due to our use of a full
automated theorem prover which allows adding arbitrary constraints in addition
to the expected Presburger formulae.
